The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-24 paper/ms.tex
minor edits

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with CFHTLS, HST Legacy Survey and UKIDSS.
The constrains are based on an abundance matching methodology using data
from cosmological N-body simulations in order to take into account the impact
of cosmic variance in our estimates.
We also measure the influence on the results of the dust extinction
scaling derived from observations by Bouwens.
We compare our results against the results of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation (GALFORM) and a hydrodynamical simulation (Illustris).
\end{abstract}

@@

\section{Observational Constraints}
\label{sec:theo}

\subsection{Dust Absorption}

This paper is based on four main observational data sets from the Hubble Space Telescope 
and three ground-based telescopes. All $z\sim 6$ LBG candidates where discovered using using 
the drop-out technique\citep{steidel03}. All magnitudes are in AB system.

The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area 
at redshift 6 corresponds 
to 740.8 arcmin$^2$ over five different lines of sight, wit a total volume of 
$1.8 \times 10^6 \textrm{Mpc}^3$.
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, $J{125}$, 
$JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
\citet{bouwens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
The Schechter parameters derived are: 
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.

>>>>

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with CFHTLS, HST Legacy Survey and UKIDSS.
The constraints are based on an abundance matching methodology to the
observational data using cosmological N-body simulations.
We also take into account the influence on the results of the dust extinction
scaling derived from observations by Bouwens.
We compare our results against the results of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation (GALFORM) and a hydrodynamical simulation (Illustris).
\end{abstract}

@@

All magnitudes are in AB system.
\section{Observational Datasets}
\label{sec:theo}

We use information from seven observational data sets.
Four obtained with the Hubble Space Telescope (HST) and three from
ground-based telescopes.
All of them select galaxy candidates at $z\sim 6$ using the drop-out
technique \citep{Steidel96}.

The data from the Hubble Space Telescope Legacy (HSTL)
\citep{bouwens14} is a compilation   of observations since the
installation of the Advanced Camera for Surveys (ACS) in 2002,
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in
2009, up to 2012.

The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area 
at redshift 6 corresponds 
to 740.8 arcmin$^2$ over five different lines of sight, wit a total volume of 
$1.8 \times 10^6 \textrm{Mpc}^3$.
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, $J{125}$, 
$JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
\citet{bouwens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
The Schechter parameters derived are: 
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.
